---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Load the data using read.csv() which will load the 'NA' values for the steps columns.  Show the summary of the obersavations.
```{r echo=TRUE}
setwd('~/Documents/repos/reproducible_resarch/RepData_PeerAssessment1')
act_tbl <- read.csv("activity.csv")
summary(act_tbl)

```


## What is mean total number of steps taken per day?
Use the *aggregate* function to sum up the steps by day.
```{r Total Steps Per Day, echo=TRUE, results='markup'}
steps_per_day <- aggregate (steps ~ date, act_tbl, sum)
head(steps_per_day)
```

#### Histogram (# of Days by Total Step bins)
```{r Distribution of Steps, echo=TRUE}
hist(steps_per_day$steps,breaks=9, ylab="# of Days", xlab="# of Steps", main="Distribution of Steps")
```

#### Mean Steps Per Day, and  Median Steps
Calculate the *mean* and *median* using the proper function.  Also, skip NA values.
``` {r Summary Stats for Steps, echo=TRUE}
mean(steps_per_day$steps, na.rm = TRUE)
median(steps_per_day$steps, na.rm = TRUE)
```


## What is the average daily activity pattern?
1. Use the *aggregate* function to get the *mean* by time interval.  
2. Store that in a data frame.
3. Plot the line chart (time series)

```{r Timeseries, echo=TRUE}
avg_intv <- aggregate (steps ~ interval, act_tbl, mean, na.rm = TRUE)
plot(avg_intv$interval,avg_intv$steps, type='l',xlab="Time Interval", ylab="mean(steps)")
```

### Time Interval with the highest average stepshea
```{r Highest Avg, echo=TRUE}
avg_intv[which (avg_intv$steps == max(avg_intv$steps)),]
```
### 
## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
