---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Load the data using read.csv() which will load the 'NA' values for the steps columns.  Show the summary of the obersavations.
```{r echo=TRUE}
setwd('~/Documents/repos/rr-1')
act_tbl <- read.csv("activity.csv")
summary(act_tbl)

```


## What is mean total number of steps taken per day?
Use the *aggregate* function to sum up the steps by day.
```{r Total Steps Per Day, echo=TRUE, results='markup'}
steps_per_day <- aggregate (steps ~ date, act_tbl, sum)
head(steps_per_day)
summary(steps_per_day)
```

#### Histogram (# of Days by Total Step bins)
```{r Distribution of Steps, echo=TRUE}
hist(steps_per_day$steps,breaks=9, ylab="# of Days", xlab="# of Steps", main="Distribution of Steps")
```

#### Mean Steps Per Day, and  Median Steps
Calculate the *mean* and *median* using the proper function.  Also, skip NA values.
``` {r Summary Stats for Steps, echo=TRUE}
mean(steps_per_day$steps, na.rm = TRUE)
median(steps_per_day$steps, na.rm = TRUE)
```
Notice that the mean() and median() steps per day did not change dramatically.  This is makes sense because we replaced NA values with the mean(steps) for that particular interval.  However, the histogram did become more centered around the mean with more days exceeding 10K steps per day.

## What is the average daily activity pattern?
1. Use the *aggregate* function to get the *mean* by time interval.  
2. Store that in a data frame.
3. Plot the line chart (time series)

```{r Timeseries, echo=TRUE}
avg_intv <- aggregate (steps ~ interval, act_tbl, mean, na.rm = TRUE)
plot(avg_intv$interval,avg_intv$steps, type='l',xlab="Time Interval", ylab="mean(steps)")
```

### Time Interval with the highest average stepshea
```{r Highest Avg, echo=TRUE}
avg_intv[which (avg_intv$steps == max(avg_intv$steps)),]
```
### 
## Imputing missing values

### Calculate the missing values
```{r Missing Values, echo=TRUE}
length( act_tbl [which (is.na(act_tbl$steps)), 1])
```
### Replace missing values
Use the mean(steps) for the interval across all days
```{r, Replace Missing values, echo=TRUE}
repl_act <- act_tbl
for (i in 1:nrow(repl_act))
{
  if (is.na (repl_act[i,1]) )
       repl_act[i,1] <- mean(repl_act[ 
           which (repl_act$interval == repl_act[i,3])  ,1], na.rm=TRUE)
}
head(repl_act)
```

### Histogram of the data with replacement data
```{r, Histogram with replacement data, echo=TRUE}
steps_per_day <- aggregate (steps ~ date, repl_act, sum)
summary(steps_per_day)
hist(steps_per_day$steps,breaks=9, ylab="# of Days", xlab="# of Steps", main="With Replacement Data")
```

## Are there differences in activity patterns between weekdays and weekends?
``` {r, Weekendays, echo=TRUE}
isWeekday <- function (d)
{
  wd <- weekdays(as.Date( as.character(d) ), abbreviate=TRUE  )

  r <- factor()
  if (wd == "Sun" || d == "Sat")
    r <- as.factor("Weekend")
  else
    r <- as.factor("Weekday")
  is
  r
  
}

repl_act$daytype <- factor( c("Weekday", "Weekend") )
for (i in 1:nrow(repl_act))
{
  repl_act[i,4] <- isWeekday(repl_act[i,2])
}
wks <- aggregate (steps ~ interval+daytype, repl_act, sum, na.rm = TRUE)

attach(wks)
library(lattice)
xyplot(steps ~ interval| daytype, 
           data = wks,
           type = "l",
           xlab = "Interval",
           ylab = "Number of steps",
           layout=c(1,2))
```
